<<<<<<< HEAD
---
title: "Hw6_201511646_나여영"
output:
  html_document: default
 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> 1. The following data were recorded for two species of irises. The objective is to develop a rule for classifying a new flower based on the four variables sl (Sepal Length), sw (Sepal Width), pl (Petal Length), pw (Petal Width).    
Provide necessary computer output to solve the following problems 1) and 2).

R에 내장되어 있는 Iris 데이터를 재구성하여 문제와 같이 복원했다.
```{r iris}

newiris=iris[51:150,]

sl<-newiris$Sepal.Length*10
sw<-newiris$Sepal.Width*10
pl<-newiris$Petal.Length*10
pw<-newiris$Petal.Width*10
sp<-newiris$Species

niris=data.frame(sl,sw,pl,pw,sp)
niris

```
                
        
                       
             
            
               
1)	Develop such a rule using the proc discrim. Try linear and quadratic discriminant functions.        

LDA
```{r MASS}

library(MASS)

index<-sample(2,size=nrow(niris), replace=T, prob=c(0.7,0.3))
train<-niris[index==1,]
test<-niris[index==2,]

#LDA
flda<-lda(sp~.,data=train)
fts1<-predict(flda, newdata=test)
tab1 <- table(test$sp, fts1$class)
mclda <- 1-sum(diag(tab1))/sum(tab1)
flda
tab1
mclda
```





QDA
```{r}
sp=as.numeric(newiris$Species)
niris=data.frame(sl,sw,pl,pw,sp)
index<-sample(2,size=nrow(niris), replace=T, prob=c(0.7,0.3))
train<-niris[index==1,]
test<-niris[index==2,]

fqda <- qda(sp~.,data=train)
fts2 <- predict(fqda,newdata=test)
tab2 <- table(test$sp,fts2$class)
mcqda <- 1-sum(diag(tab2))/sum(tab2)
fqda
tab2
mcqda
```





2)	A new iris is discovered use your results to classify the new species into one of these two groups. The new data are sl=60, sw=25, pl=40, pw=11. Use linear discriminant functions with c(1|2)=c(2|1) and P1=P2.

```{r}
newd=data.frame(sl=60,sw=25,pl=40,pw=11)
predict(flda, newdata = newd)
```












=======
---
title: "Hw6_201511646_나여영"
output:
  html_document: default
 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> 1. The following data were recorded for two species of irises. The objective is to develop a rule for classifying a new flower based on the four variables sl (Sepal Length), sw (Sepal Width), pl (Petal Length), pw (Petal Width).    
Provide necessary computer output to solve the following problems 1) and 2).

R에 내장되어 있는 Iris 데이터를 재구성하여 문제와 같이 복원했다.
```{r iris}

newiris=iris[51:150,]

sl<-newiris$Sepal.Length*10
sw<-newiris$Sepal.Width*10
pl<-newiris$Petal.Length*10
pw<-newiris$Petal.Width*10
sp<-newiris$Species

niris=data.frame(sl,sw,pl,pw,sp)
niris

```
                
        
                       
             
            
               
1)	Develop such a rule using the proc discrim. Try linear and quadratic discriminant functions.        

LDA
```{r MASS}

library(MASS)

index<-sample(2,size=nrow(niris), replace=T, prob=c(0.7,0.3))
train<-niris[index==1,]
test<-niris[index==2,]

#LDA
flda<-lda(sp~.,data=train)
fts1<-predict(flda, newdata=test)
tab1 <- table(test$sp, fts1$class)
mclda <- 1-sum(diag(tab1))/sum(tab1)
flda
tab1
mclda
```





QDA
```{r}
sp=as.numeric(newiris$Species)
niris=data.frame(sl,sw,pl,pw,sp)
index<-sample(2,size=nrow(niris), replace=T, prob=c(0.7,0.3))
train<-niris[index==1,]
test<-niris[index==2,]

fqda <- qda(sp~.,data=train)
fts2 <- predict(fqda,newdata=test)
tab2 <- table(test$sp,fts2$class)
mcqda <- 1-sum(diag(tab2))/sum(tab2)
fqda
tab2
mcqda
```





2)	A new iris is discovered use your results to classify the new species into one of these two groups. The new data are sl=60, sw=25, pl=40, pw=11. Use linear discriminant functions with c(1|2)=c(2|1) and P1=P2.

```{r}
newd=data.frame(sl=60,sw=25,pl=40,pw=11)
predict(flda, newdata = newd)
```












>>>>>>> 704346157696d5c879444e5bc135c15fa187d2e1
