<<<<<<< HEAD
---
title: "hw7_Clustering"
author: "201511646_나여영"
date: "2017년 11월 27일"
 
output: 
  pdf_document: 
    keep_tex: yes
    latex_engine: xelatex
mainfont: NanumGothic
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##HW7_Clustering_201511646

>1. In this example, we have distances between ten American cities based on the flying mileages between them. The objective is to see if we can define clusters of these cities based on the distances.

```{r}
```{r }
Atlanta<-c(0,587,1212,701,1936,604,748,2139,2182,543)
Chicago<-c(587,0,920,940,1745,1188,713,1858,1737,597)
Denver<-c(1212,920,0,879,831,1726,1631,949,1021,1494)
Houston<-c(701,940,879,0,1374,968,1420,1645,1891,1220)
LA<-c(1936,1745,831,1374,0,2339,2451,347,959,2300)
Miami<-c(604,1188,1726,968,2339,0,1092,2594,2734,923)
Newyork<-c(748,713,1631,1420,2451,1092,0,2571,2408,205)
Sanfrancisco<-c(2139,1858,949,1645,347,2594,2571,0,678,2442)
Seattle<-c(2182,1737,1021,1891,959,2734,2408,678,0,2329)
WashingtonDC<-c(543,597,1494,1220,2300,923,205,2442,2329,0)
```


다음은 대칭행렬이 맞는지 확인하는 과정이다
```{r dplyr}
cities<-matrix(c(Atlanta,Chicago,Denver, Houston,LA, Miami, Newyork,Sanfrancisco, Seattle, WashingtonDC),10,byrow=T)
cities
Tcities=t(cities)

library(dplyr)
all_equal(cities, Tcities)
```
맞는지 확인했으므로 그 후 scatter plot을 확인해 데이터의 분포를 본다.
```{r}
colnames(cities)<-c("Atlanta","Chicago","Denver", "Houston","LA", "Miami", "Newyork","Sanfrancisco", "Seattle", "WashingtonDC")
rownames(cities)<-c("Atlanta","Chicago","Denver", "Houston","LA", "Miami", "Newyork","Sanfrancisco", "Seattle", "WashingtonDC")

plot(cities,pch = 19, xlab = c("x coordinate"), ylab = c("y coordinate"),main = "Scatter plot of Cities")
text(cities, labels = abbreviate(colnames(cities)), cex = 0.8, pos = 3, col = "blue") # pos=1 : at the bottom

```


> 1) Do the cluster analysis using (1) single linkage, (2) average linkage and (3) the centroid method.  

(1)single linkage
```{r}
hc1_cities<-hclust(dist(cities, method="euclidian")^2, method="single")
hc1_cities
rev(hc1_cities) #height : 군집간 거리 / merge: 병합순

```




=======
---
title: "hw7_Clustering"
author: "201511646_나여영"
date: "2017년 11월 27일"
 
output: 
  pdf_document: 
    keep_tex: yes
    latex_engine: xelatex
mainfont: NanumGothic
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##HW7_Clustering_201511646

>1. In this example, we have distances between ten American cities based on the flying mileages between them. The objective is to see if we can define clusters of these cities based on the distances.

```{r}
```{r }
Atlanta<-c(0,587,1212,701,1936,604,748,2139,2182,543)
Chicago<-c(587,0,920,940,1745,1188,713,1858,1737,597)
Denver<-c(1212,920,0,879,831,1726,1631,949,1021,1494)
Houston<-c(701,940,879,0,1374,968,1420,1645,1891,1220)
LA<-c(1936,1745,831,1374,0,2339,2451,347,959,2300)
Miami<-c(604,1188,1726,968,2339,0,1092,2594,2734,923)
Newyork<-c(748,713,1631,1420,2451,1092,0,2571,2408,205)
Sanfrancisco<-c(2139,1858,949,1645,347,2594,2571,0,678,2442)
Seattle<-c(2182,1737,1021,1891,959,2734,2408,678,0,2329)
WashingtonDC<-c(543,597,1494,1220,2300,923,205,2442,2329,0)
```


다음은 대칭행렬이 맞는지 확인하는 과정이다
```{r dplyr}
cities<-matrix(c(Atlanta,Chicago,Denver, Houston,LA, Miami, Newyork,Sanfrancisco, Seattle, WashingtonDC),10,byrow=T)
cities
Tcities=t(cities)

library(dplyr)
all_equal(cities, Tcities)
```
맞는지 확인했으므로 그 후 scatter plot을 확인해 데이터의 분포를 본다.
```{r}
colnames(cities)<-c("Atlanta","Chicago","Denver", "Houston","LA", "Miami", "Newyork","Sanfrancisco", "Seattle", "WashingtonDC")
rownames(cities)<-c("Atlanta","Chicago","Denver", "Houston","LA", "Miami", "Newyork","Sanfrancisco", "Seattle", "WashingtonDC")

plot(cities,pch = 19, xlab = c("x coordinate"), ylab = c("y coordinate"),main = "Scatter plot of Cities")
text(cities, labels = abbreviate(colnames(cities)), cex = 0.8, pos = 3, col = "blue") # pos=1 : at the bottom

```


> 1) Do the cluster analysis using (1) single linkage, (2) average linkage and (3) the centroid method.  

(1)single linkage
```{r}
hc1_cities<-hclust(dist(cities, method="euclidian")^2, method="single")
hc1_cities
rev(hc1_cities) #height : 군집간 거리 / merge: 병합순

```




>>>>>>> 704346157696d5c879444e5bc135c15fa187d2e1
